---
title: "Activity: Combining Datasets (Answer Key)"
author: "Rodrigo Zamith"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: true
    code_folding: show
    df_print: paged
    theme: spacelab
    highlight: pygment
---

### Load Data

```{r}
library(tidyverse)
vaccines_orig <- read_csv("https://raw.githubusercontent.com/sociepy/covid19-vaccination-subnational/main/data/vaccinations.csv")
population_orig <- read_csv("https://raw.githubusercontent.com/sociepy/covid19-vaccination-subnational/main/data/population.csv")

vaccines_orig %>%
  select(-total_vaccinations_per_100, -people_vaccinated_per_100, -people_fully_vaccinated_per_100) %>%
  write_csv("/tmp/vaccinations_by_country_20210311.csv")

population_orig %>%
  group_by(region_iso) %>%
  summarize(population=as.integer(median(population))) %>%
  write_csv("/tmp/population_by_country_20210311.csv")
```


```{r}
library(tidyverse)
vaccines <- read_csv("/tmp/vaccinations_by_country_20210311.csv")
population <- read_csv("/tmp/population_by_country_20210311.csv")

vaccines <- read_csv("https://zamith.umasscreate.net/data/vaccinations_by_country_20210311.csv")
population <- read_csv("https://zamith.umasscreate.net/data/population_by_country_20210311.csv")
```

### Let's take a look at our data

```{r}
vaccines
```

```{r}
population
```

### Join the Data

> I want to add the associated information from the `population` variable (from the `population` data frame) to each observation in my `vaccines` data frame. How would I do that?

```{r}
vaccines_with_pop <- left_join(vaccines, population, by="region_iso")
```

### Compute a Variable

> Calculate a per 1,000 people rate for the number of people vaccinated in each **country**.

```{r}
vaccines_with_pop %>%
  group_by(location) %>%
  summarize(total_people_vac=sum(people_vaccinated, na.rm=TRUE), population=sum(population)) %>%
  filter(total_people_vac>0) %>%
  mutate(people_vac_per_1k=total_people_vac/population*1000)
```

### Create a bar chart

> Create a bar graph with the 10 countries that have the highest vaccination rates

```{r}
vaccines_with_pop %>%
  group_by(location) %>%
  summarize(total_people_vac=sum(people_vaccinated, na.rm=TRUE), population=sum(population)) %>%
  filter(total_people_vac>0) %>%
  mutate(people_vac_per_1k=total_people_vac/population*1000) %>%
  top_n(10, people_vac_per_1k) %>%
  ggplot(aes(x=fct_reorder(location, people_vac_per_1k), y=people_vac_per_1k)) +
    geom_col() +
    coord_flip()
```
