---
title: "Activity: Combining Datasets"
author: "YOUR NAME"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: true
    code_folding: show
    df_print: paged
    theme: spacelab
    highlight: pygment
---

### Load Data

```{r}
library(tidyverse)
vaccines <- read_csv("https://zamith.umasscreate.net/data/vaccinations_by_country_20210311.csv")
population <- read_csv("https://zamith.umasscreate.net/data/population_by_country_20210311.csv")
# These data are modified extracts of files obtained from/aggregated by SociePy (see: https://github.com/sociepy/covid19-vaccination-subnational)
```

### Let's take a look at our data

```{r}
vaccines
```

```{r}
population
```

### Join the Data

> I want to add the associated information from the `population` variable (from the `population` data frame) to each observation in my `vaccines` data frame. How would I do that?

```{r}
# Code here
```

### Compute a Variable

> Calculate a per 1,000 people rate for the number of people vaccinated in each **country**.

```{r}
# Code here
```

### Create a bar chart

> Create a bar graph with the 10 countries that have the highest vaccination rates

```{r}
# Code here
```
