---
title: "Activity: Extracting Data From PDFs"
author: "YOUR NAME"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: true
    code_folding: show
    df_print: paged
    theme: spacelab
    highlight: pygment
---

### Question 1

> Read the _cleaned_ CSV file you just created into an object called `umass_data`.

Briefly explain what you are trying to do here. (Write this before you even write any code. For example, in this case, you might say: "I need to load the `tidyverse` package, which contains the `read_csv()` function that I need to import the CSV file I created. I'll be assigning the output of that function to an object called `umass_data`." The purpose of this segment is to get you to create a roadmap in your head _before_ you try to execute it.)

```{r}
# Provide your code here.
```

### Question 2

> Check the structure of your `umass_data` object. What is the name of the variable (column) containing information about students who are Hispanic/Latino of any race? What is data type for that variable?

Briefly explain what you are trying to do (or looking for) here.

```{r}
# Provide your code here.
```

Provide your response here.

### Question 3

> What is the range of values for the variable containing information about the number of Asian students?

Briefly explain what you are trying to do (or looking for) here.

```{r}
# Provide your code here.
```

Provide your response here.

### Question 4

> What is the mean of the variable for Black/African American students? What do you need to keep in mind about the source data when answering this question? (Hint: Look back to the PDF file and see if there are any methodological notes you need to be mindful of here.)

Briefly explain what you are trying to do (or looking for) here.

```{r}
# Provide your code here.
```

Offer a clear **answer** here.
