---
title: "Course Exercise #2"
author: "YOUR NAME (with ANY PARTNERS)"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: true
    code_folding: show
    df_print: paged
    theme: spacelab
    highlight: pygment
---

### Load the Data

```{r}
options(scipen=999)
library(tidyverse)
cafi <- read_csv("https://zamith.umasscreate.net/data/cafi_data.csv")
```

### Question 1

Briefly explain what you are trying to do here.

```{r}
# Provide your code here.
```

Offer a clear **answer** here.

### Question 2

Briefly explain what you are trying to do here.

```{r}
# Provide your code here.
```

Offer a clear **answer** here.

### Question 3

Briefly explain what you are trying to do here.

```{r}
# Provide your code here.
```

Offer a clear **answer** here.

### Question 4

Briefly explain what you are trying to do here.

```{r}
# Provide your code here.
```

Offer a clear **answer** here.

### Question 5

Briefly explain what you are trying to do here.

```{r}
# Provide your code here.
```

Offer a clear **answer** here.

### Question 6

Briefly explain what you are trying to do here.

```{r}
# Provide your code here.
```

Offer a clear **answer** here.

### Question 7

Briefly explain what you are trying to do here.

```{r}
# Provide your code here.
```

Offer a clear **answer** here.

### Question 8 (Part 1)

My question: 

My rationale: 

```{r}
# Provide your code here.
```

Offer a clear **answer** here.

### Question 8 (Part 2)

My question: 

My rationale: 

```{r}
# Provide your code here.
```

Offer a clear **answer** here.