---
title: "Course Exercise #2"
author: "YOUR NAME (with ANY PARTNERS)"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: true
    code_folding: show
    df_print: paged
    theme: spacelab
    highlight: pygment
---

### Load the Data

```{r}
options(scipen=999)
library(tidyverse)
cafi <- read_csv("https://zamith.umasscreate.net/data/cafi_data.csv")
```

### Question 1

A good way to approach this question would be to:

1. Check the first few observations.
2. Check the structure of the data frame.
3. Check the summary data for the data frame.

```{r}
head(cafi)
str(cafi)
summary(cafi)
```

Overall, these data seem to be in pretty good shape. However, one thing that strikes me is that there is a decent amount of `NA` values for some of the variables (e.g., `Total Football Coaching Salaries`).

### Question 2

Here's what I'd need to do:

1. Load my data frame.
2. Apply a filter to only include year 2018 and only evaluate schools.
3. Sort the data based on the Coach's Compensation.

```{r}
cafi %>%
  filter(Year==2018) %>%
  arrange(-`Coaches Compensation`) %>%
  select(Entity, Year, `Coaches Compensation`) %>%
  head()
```

**The Ohio State University** had the highest compensation for its athletic coaches.

### Question 3

Briefly explain what you are trying to do here.

```{r}
cafi %>%
  filter(Entity %in% c("The Ohio State University", "University of Massachusetts Amherst") & Year==2018) %>%
  select(Entity, Year, `Coaches Compensation`)

40242782-6515645

(40242782-6515645)/6515645*100
```

The Ohio State University's compensation for its athletic coaches was **$33,727,137** (or **517.6%**) higher than UMass'.

### Question 4

```{r}
cafi %>%
  filter(`FBS Conference` %in% c("Southeastern Conference", "Big Ten Conference") & Year==2018) %>%
  group_by(`FBS Conference`) %>%
  summarize(total_football_spending=sum(`Total Football Spending`))
```

The Southeastern Conference had **higher** total football expenditures than the Big Ten Conference.

### Question 5

```{r}
cafi %>%
  filter(Year==2018 & `FBS Conference` %in% c("Atlantic Coast Conference", "Big Ten Conference", "Big 12 Conference", "Pacific-12 Conference", "Southeastern Conference")) %>%
  group_by(`FBS Conference`) %>%
  summarize(median_total_football_spending=median(`Total Football Spending`)) %>%
  arrange(-median_total_football_spending)
```

The **Southeastern Conference** had the highest median total football spending among its schools in 2018.

### Question 6

```{r}
cafi %>%
  filter(between(Year, 2013, 2018) & `FBS Conference` %in% c("Atlantic Coast Conference", "Big Ten Conference", "Big 12 Conference", "Pacific-12 Conference", "Southeastern Conference")) %>%
  select(Year, `FBS Conference`, `Total Football Spending`) %>%
  ggplot(aes(x=fct_reorder(`FBS Conference`, desc(`FBS Conference`)), y=`Total Football Spending`)) +
    geom_boxplot() +
    coord_flip() +
    facet_wrap(~Year) +
    theme(axis.text.x=element_text(angle=45, hjust=1)) +
    xlab("FBS Conference")
```
I can see that the median total football spending by the Southeastern Conference has routinely exceeded that of the other Power Five Conferences, and it made a _significant_ jump in 2018. Additionally, football spending has increased across the board in recent years.

### Question 7

```{r}
cafi %>%
  filter(Entity=="University of Massachusetts Amherst") %>%
  arrange(Year) %>%
  select(Entity, Year, `Total Expenses`) %>%
  mutate(pct_change=(`Total Expenses`-lag(`Total Expenses`, 1))/lag(`Total Expenses`, 1)*100) %>%
  filter(between(Year, 2013, 2018))
```

The increases between 2013 and 2018 were: **2.8%, 7.2%, 10.1%, 14.5%, 11.1%, and -2.3%**.

### Question 8 (Part 1)

My question: Has UMass' academic spending increased at a proportional rate to its athletic spending over the past five years?

Rationale: I believe this is an interesting question because it sheds light on UMass' spending priorities, especially in light of tightening budgets and increased enrollment costs in higher education.

```{r}
cafi %>%
  filter(Entity=="University of Massachusetts Amherst") %>%
  arrange(Year) %>%
  select(Entity, Year, `Total Expenses`, `Total Academic Spending (University-Wide)`) %>%
  mutate(pct_chg_athletic=(`Total Expenses`-lag(`Total Expenses`, 1))/lag(`Total Expenses`, 1)*100, pct_chg_acad=(`Total Academic Spending (University-Wide)`-lag(`Total Academic Spending (University-Wide)`, 1))/lag(`Total Academic Spending (University-Wide)`, 1)*100) %>%
  mutate(pct_diff=pct_chg_athletic-pct_chg_acad) %>%
  filter(between(Year, 2014, 2018))
```

With the exception of the most recent year (2018), UMass has seen larger year-over-year percent increases in its total athletic spending.

### Question 8 (Part 2)