---
title: "Course Exercise #3"
author: "Rodrigo Zamith"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: true
    code_folding: show
    df_print: paged
    theme: spacelab
    highlight: pygment
---

### Load the Data

```{r}
options(scipen=999)
library(tidyverse)
# ppp_ma_small <- read_csv("/tmp/All Data 0808/All Data 0808/Massachusetts 0808/PPP Data up to 150k 080820 MA.csv", col_types = cols(.default = "c"))
# ppp_all <- read_csv("/tmp/All Data 0808/All Data 0808/150k plus 0808/PPP Data 150k plus 080820.csv", col_types = cols(.default = "c"))
# ppp_ma <- ppp_all %>%
#   filter(State=="MA") %>%
#   bind_rows(ppp_ma_small)
# 
# library(lubridate)
# ppp_ma %>%
#   select(BusinessName, BusinessType, Address, City, State, Zip, NAICSCode, RaceEthnicity, Gender, Veteran, NonProfit, JobsReported, DateApproved, Lender, CD, LoanRange, LoanAmount) %>%
#   mutate(RaceEthnicity=na_if(RaceEthnicity, "Unanswered"), Gender=na_if(Gender, "Unanswered"), Veteran=na_if(Veteran, "Unanswered"), NonProfit=recode(NonProfit, "Y"="Yes"), JobsReported=as.numeric(JobsReported), DateApproved=mdy(DateApproved), LoanRange=recode(LoanRange, "a $5-10 million"="$5-10 million", "b $2-5 million"="$2-5 million", "c $1-2 million"="$1-2 million", "d $350,000-1 million"="$350,000-1 million", "e $150,000-350,000"="$150,000-350,000"), LoanAmount=as.numeric(LoanAmount), City=str_to_title(City), Address=str_to_title(Address)) %>%
#   write_csv("/tmp/ppp_loans_ma.csv")

ppp_ma <- read_csv("https://zamith.umasscreate.net/data/ppp_loans_ma.csv", col_types=cols(LoanAmount="d"))
naics_codes <- read_csv("https://zamith.umasscreate.net/data/naics_2017.csv")
city_standardized <- read_csv("https://zamith.umasscreate.net/data/ppp_cities_standardized_names.csv")
```

### Combining Data

Briefly explain what you are trying to do here.

```{r}
ppp_ma_joined <- ppp_ma %>% left_join(naics_codes, by=c("NAICSCode"="id")) %>% rename(NAICSName=name) %>% left_join(city_standardized, by="City")
```

### Data Analysis

#### Question #1

> Write your interview question here.

```{r}
# Write your code here
```

What is the **answer** to your question?

#### Question 2

> Write your interview question here.

```{r}
# Write your code here
```

What is the **answer** to your question?

#### Question 3

> Write your interview question here.

```{r}
# Write your code here
```

What is the **answer** to your question?

#### Question 4

> Write your interview question here.

```{r}
# Write your code here
```

What is the **answer** to your question?

#### Question 5

> Write your interview question here.

```{r}
# Write your code here
```

What is the **answer** to your question?

### Short Article (400-500 words)

(I suggest writing this in Word or some other software that supports spell- and grammar-checking, and then copy and pasting your story in.)

### List of Interviewees

#### Interviewee #1

- Name, Title/Position, Organization
- Contact information (e.g., phone number or e-mail)
- URL to a page with details about them (e.g., biography page, personal website)
- Specifics about what you think they could add to your brief (e.g., a specific finding you think they could help contextualize, and why you think they'd have the expertise/lived experience to do that)

- First interview question you'd ask them. (Be sure to phrase these in an appropriate way.)
- Second interview question you'd ask them. (Be sure to phrase these in an appropriate way.)
- Third interview question you'd ask them. (Be sure to phrase these in an appropriate way.)

#### Interviewee #2

- Name, Title/Position, Organization
- Contact information (e.g., phone number or e-mail)
- URL to a page with details about them (e.g., biography page, personal website)
- Specifics about what you think they could add to your brief (e.g., a specific finding you think they could help contextualize, and why you think they'd have the expertise/lived experience to do that)

- First interview question you'd ask them. (Be sure to phrase these in an appropriate way.)
- Second interview question you'd ask them. (Be sure to phrase these in an appropriate way.)
- Third interview question you'd ask them. (Be sure to phrase these in an appropriate way.)