---
title: "Course Exercise #3"
author: "Rodrigo Zamith"
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float: true
    code_folding: show
    df_print: paged
    theme: spacelab
    highlight: pygment
---

### Load the Data

```{r}
options(scipen=999)
library(tidyverse)
ppp_ma <- read_csv("https://zamith.umasscreate.net/data/ppp_loans_ma.csv", col_types=cols(LoanAmount="d"))
naics_codes <- read_csv("https://zamith.umasscreate.net/data/naics_2017.csv")
city_standardized <- read_csv("https://zamith.umasscreate.net/data/ppp_cities_standardized_names.csv")
```

Let's confirm that the data were imported correctly:

```{r}
head(ppp_ma)
head(naics_codes)
head(city_standardized)
```


### 1. Combining Data

Briefly explain what you are trying to do here.

```{r}
ppp_ma_joined <- ppp_ma %>% left_join(naics_codes, by=c("NAICSCode"="id")) %>% rename(NAICSName=name) %>% left_join(city_standardized, by="City")
```

### 2. Data Analysis

#### Question #1

> Write your (data) interview question here.

```{r}
# Write your code here
```

What is the **answer** to your question?

#### Question #2

> Write your (data) interview question here.

```{r}
# Write your code here
```

What is the **answer** to your question?

#### Question #3

> Write your (data) interview question here.

```{r}
# Write your code here
```

What is the **answer** to your question?

#### Question #4

> Write your (data) interview question here.

```{r}
# Write your code here
```

What is the **answer** to your question?

#### Question #5

> Write your (data) interview question here.

```{r}
# Write your code here
```

What is the **answer** to your question?

### 3. Short Article (400-500 words)

(I suggest writing this in Word or some other software that supports spell- and grammar-checking, and then copy and pasting your story in.)

### 4. The Interviewees

#### Interviewee #1

- Name, Title/Position, Organization
- Contact information (e.g., phone number or e-mail)
- URL to a page with details about them (e.g., biography page, personal website)
- Specifics about what you think they could add to your article (e.g., a specific finding you think they could help contextualize, and why you think they'd have the expertise/lived experience to do that)

- First interview question you'd ask them. (Be sure to phrase these in an appropriate way.)
- Second interview question you'd ask them. (Be sure to phrase these in an appropriate way.)
- Third interview question you'd ask them. (Be sure to phrase these in an appropriate way.)

#### Interviewee #2

- Name, Title/Position, Organization
- Contact information (e.g., phone number or e-mail)
- URL to a page with details about them (e.g., biography page, personal website)
- Specifics about what you think they could add to your article (e.g., a specific finding you think they could help contextualize, and why you think they'd have the expertise/lived experience to do that)

- First interview question you'd ask them. (Be sure to phrase these in an appropriate way.)
- Second interview question you'd ask them. (Be sure to phrase these in an appropriate way.)
- Third interview question you'd ask them. (Be sure to phrase these in an appropriate way.)
